Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex

A known result is that a power series of matrices converges iff the eigenvalues of the matrix are less than 1.

\todo[inline]{complete this, show convergence}

>>>>

A known result is that a power series of matrices converges~\cite{horn1990matrix} iff the eigenvalues of the matrix are less than 1, to the following:
\begin{align*}
\sum_{i=0}^{\inf}T^i  &= (I - T)^-1
\end{align*}
Where $I$ is the identity matrix and $T$ is a square matrix. Thus, our system will converge

\begin{align*}
x_{\inf} &= 0 + (I - A_d + B_dK)^-1\B_dk\delta
\end{align*}

Hence, provided $(I - A_d + B_dK)^-1\B_dk\delta$ is within the safe space, our fixed point controller system is stable, in that it converges to a finite value, although not asymptomatically stable because it doesn't converge to the origin.
